Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite

### 2021-05-20 paper2020/talk.tex
who done what

\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usetikzlibrary{fadings}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{intersections}

@@

\begin{frame}
  \begin{itemize}
  \item 
    Our starting point is the FraCoq system (Presented by the same authors at IWCS 2017 with updates at NoDaliDa 2019):

\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=4.2cm,
                    semithick,scale=0.65, every node/.style={transform shape}]
  \tikzstyle{every state}=[draw=black,text=black,shape=rectangle]

 \node[state]         (txt)                {Textual Problem};
 \node[state]         (ast) [right of=txt] {AST};
 \node[state]         (pp)  [right of=ast] {Logic Form};
 \node[state]         (math)    [right of=pp]  {Checked result};

@@

 \node[state]         (proof) [above of=Coq]  {Proof};
 \path  (proof) edge                (Coq);

\end{tikzpicture}
\item
In this paper we update the \alert{Semantics} with {Temporal Semantics}. We achieve coverage of 329 out of 337 problems in the FraCaS test suite, with an accuracy of 81\%.
  \end{itemize}
\end{frame}

>>>>

\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}
\usetikzlibrary{fadings}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{intersections}
\usetikzlibrary{positioning}

@@

\begin{frame}
  \begin{itemize}
  \item 
    Our starting point is the FraCoq system (Presented by the same authors at IWCS 2017 with updates at NoDaliDa 2019): \\
    \bigskip
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=4.2cm,
                    semithick,scale=0.63, every node/.style={transform shape},inputnode/.style={draw=black,text=black,shape=rectangle,rounded corners=1mm}]
  \tikzstyle{every state}=[draw=black,text=black,shape=rectangle]

 \node[inputnode]         (txt)                {Textual Problem};
 \node[state]         (ast) [right of=txt] {AST};
 \node[state]         (pp)  [right of=ast] {Logic Form};
 \node[state]         (math)    [right of=pp]  {Checked result};

@@

 \node[inputnode]         (proof) [above of=Coq,node distance=2cm]  {Proof};
 \path  (proof) edge                (Coq);
 \node               (peter) [above of=GF,node distance=3cm]  {[Ljunglöf 2011]};
 \path  (peter) edge                (GF);
 \node               (cooper) [above of=txt,node distance=2cm]  {[Cooper \textit{et al.} 1996]};
 \path  (cooper) edge                (txt);

\end{tikzpicture}
    \medskip
\item
In this paper we update the \alert{Semantics} with {Temporal Semantics}. We achieve coverage of 329 out of 337 problems in the FraCaS test suite, with an accuracy of 81\%.
  \end{itemize}
\end{frame}
